TO CHANGE: Web Service Community \\ Learning

### 2014-07-11 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{The Join Challenge}\label{s:tjc}
Sometimes web services can increase their overall utility by starting a collaboration with other web services as communities. This collaboration can help them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters. The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration.

\subsection{Join Consequences}\label{s:jc}

>>>>

\subsection{The Join Challenge}\label{s:tjc}
Sometimes web services can increase their overall utility by starting a collaboration with other web services as communities. This collaboration can help them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters and long-term outcome is dependent on these parameters.

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy between all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities.
\subsection{Join Consequences}\label{s:jc}
